\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{positioning}
\usepackage{fancyvrb}
\begin{document}
\section*{Raven Stare Down}

\begin{center}
  \begin{tikzpicture}
    \draw[line width=0.4mm] (0,0) circle (.5cm);
    \draw[line width=0.75mm,rotate=-1.5] (0,-1) -- (0,0.5);
    \draw[line width=0.75mm,rotate=-1.5] (0.1,-1) -- (0.1,0.5);
    \draw[line width=0.75mm,rotate=1.5] (-0.1,-1) -- (-0.1,0.5);
    \draw[line width=0.75mm,rotate=-1.5] (0.2,-1) -- (0.2,0.5);
    \draw[line width=0.75mm,rotate=1.5] (-0.2,-1) -- (-0.2,0.5);
    \draw[line width=0.75mm,rotate=1.5] (-0.3,-0.9) -- (-0.3,0.4);
    \draw[line width=0.75mm,rotate=1.5] (-0.2,-0.8) -- (-0.2,0.3);
    \draw[line width=0.75mm,rotate=1.5] (-0.4,-0.8) -- (-0.4,0.3);
    \draw[line width=0.75mm,rotate=-1.5] (0.4,-0.8) -- (0.4,0.3);
    \draw[line width=0.75mm,rotate=-1.5] (0.3,-0.9) -- (0.3,0.4);
    \draw[line width=0.75mm,rotate=1.5] (-0.3,-0.9) -- (-0.3,0.4);
    
    \draw[line width=0.75mm,rotate=1.5] (-0.48,-0.7) -- (-0.48,0.2);
    \draw[line width=0.75mm,rotate=-1.5] (0.48,-0.7) -- (0.48,0.2);
    \draw[line width=0.4mm] (0,-1.2) ellipse (10pt and 20pt);
    \draw[line width=0.4mm] (0,-1.9) ellipse (15pt and 10pt);
    %\draw[fill=white,color=white] (0,-1.9) ellipse (13pt and 8pt);
    \draw[fill=white,color=white] (0,-1.5) ellipse (8pt and 8pt);
  \end{tikzpicture}
\end{center}

\begin{center}
  \begin{tikzpicture}
    \draw[fill=white,color=white] (0,-1.5) ellipse (8pt and 8pt);
  \end{tikzpicture}
\end{center}


\begin{center}
  \begin{tikzpicture}
    \draw[fill=black] (0.4,-0.1) ellipse (8pt and 4pt);%(0.4,0) circle (.2cm);
    \draw (0.4,0) -- (0.4,-0.15) -- (-0.2,-0.1)-- (0.4,0);
    \draw[fill=white] (0.34,-0.05) circle(.05cm);
    \draw[rotate=-16,fill=black] (1,-0.2) ellipse (17pt and 8pt);
    \draw[rotate=-16,fill=black] (1,0) rectangle (2,-0.05);
    \draw[rotate=-16,fill=black] (1,-0.07) rectangle (2,-0.12);
    \draw[line width=0.25mm] (0.8,-1.1) -- (0.9,-0.5);
    \draw[line width=0.15mm] (0.8,-1.1) -- (0.7,-1.15);
    \draw[line width=0.15mm] (0.8,-1.1) -- (0.8,-1.2);
    
    \draw[line width=0.25mm] (0.9,-1.1) -- (0.9,-0.5);
    \draw[line width=0.15mm] (0.9,-1.1) -- (0.85,-1.2);
    \draw[line width=0.15mm] (0.9,-1.1) -- (0.92,-1.2);
    
  \end{tikzpicture}
\end{center}

Egwene faces due north
as she rests, sitting in the thick grass of Edmond's Field.
The unobstructive meadow helps her to scout out any nosy ravens
that might cast unfavorable shade on today's shearing event.

She sits unmoved
as a raven passes from behind her,
hopping westward in a straight line.

The bird is at its closest distance to Egwene at 30 WL (Westland) feet.

Unbeknownst to the raven, Egwene has a 210 degree horizontal field
of view and will see the raven as it crosses into her viewing angle.

Once the bird walks into her field of view, then the staring contest
can commence; and ultimately upon seeing Egwene's scowl
the snoopy bird will depart.

\textit{Assuming that the raven walks in a straight line
and that Egwene will only move her eyes
to reach a maximal 210 degree viewing angle},
how far in WL feet will the bird need to hop
in order for it to become visible to Egwene?


\subsection*{EOTW -1}  %\textbf{eotw -1}
\textit{ Set in The Eye of the World $>$ Earlier Ravens Prologue } \pagebreak

\section*{Heal the Corrupted Memory}

\begin{tikzpicture}
  [mat/.style={matrix of nodes,
      nodes={draw, minimum size=10mm, minimum width=15mm, anchor = north},
      column sep=-\pgflinewidth,
      row sep=0.5mm,
      nodes in empty cells,
      row 1 column 1/.style={nodes={draw=none}},
      row 1 column 2/.style={nodes={draw=none}},
      row 1 column 3/.style={nodes={draw=none}},
      row 3 column 1/.style={nodes={draw=none}},
      row 3 column 2/.style={nodes={draw=none}},
      row 3 column 3/.style={nodes={draw=none}},
  }]
  \matrix[mat] (array)
         {
           Lews  & &     \\
           :     & -     & )\\
           K()+0 & K()+1 & K()+2\\
         };
\end{tikzpicture}


\noindent \begin{tikzpicture}
  [mat/.style={matrix of nodes,
      nodes={draw, minimum size=10mm, minimum width=15mm, anchor = north},
      column sep=-\pgflinewidth,
      row sep=0.5mm,
      nodes in empty cells,
      row 1 column 1/.style={nodes={draw=none}},
      row 1 column 2/.style={nodes={draw=none}},
      row 1 column 3/.style={nodes={draw=none}},
      row 3 column 1/.style={nodes={draw=none}},
      row 3 column 2/.style={nodes={draw=none}},
      row 3 column 3/.style={nodes={draw=none}},
  }]
  \matrix[mat] (array)
         {
           Elan  & &     \\
           X     & \raisebox{-3ex}{\underline{\hspace{0.4cm}}} & X \\
           K()+0 & K()+1                                       & K()+2\\
         };
\end{tikzpicture}


Lews Therin is joyously searching for his wife
inside his charred palace as he stands
next to the corpses of all his own kin who had met their fatal end,
and is found to be in a state of mindless bliss
as Elan Morin Tedronai appears.

As they exchange words Elan becomes aware that
Lews is ignorant to the fact that Lews had
performed this murderous act.

Lews' memory about what has happened to his kinsfolk has been corrupted.
Elan has the real memory that can be employed to heal Lews' corrupted
version of events.
Assume that the memory of the event is stored as a 3-letter happy \texttt{:-)} emoticon
in Lews' memory and can be healed by Elan's real memory,
indicated by a dead person \texttt{X\_X} emoticon.

Healing can be performed 1 letter at a time; each letter of the
emoticon components reside in their own memory unit as an adjoined sequence
in both Elan's and Lews' memory.

There are 3 magical functions that can be combined in a way
to fully heal Lews' memory.
What is the order of functions performed,
spelled out as a pronounceable spell
that will heal Lews' memory?\\
\hspace*{0.8cm}\textbf{spell: \_\ \_\ \_\ \_\ \_\ \_}

\noindent Functions:\\
\hspace*{0.2cm} - \hspace*{0.2cm}\textbf{H()} heals 1 letter memory unit at the paired position.\\
\hspace*{0.2cm} - \hspace*{0.2cm}\textbf{I()} increments the paired healing position forward 1 letter in memory.\\
\hspace*{0.2cm} - \hspace*{0.2cm}\textbf{K()} positions the paired healing position to start at the kinsfolk memory.

\subsection*{EOTW 0}
\textit{ Set in The Eye of the World $>$ Prologue Dragonmount }  \pagebreak

\section*{Wind-blocking Cloak}

The dark rider that has been following Rand and Tam down the Westwood road
stops to light a fire.

His cloak has been appearingly immovable in spite of heavy wind. Let's assume
that it is the cloak's weight that is causing the immovability, with equal
weight being distributed throughout the fabric.

The rider removes his cloak and ties it to branches on a nearby tree
just in the right spot so it will
\textbf{block the wind}* when he lights the fire.

Assume that he had performed a magic spell that gave extra magic weights
to what was previously a normal fabric coat, but that he did so
without any wasted magic. Assume force of gravity and force of the wind
are the only forces acting on the cloak (ignoring any air resistance/drag,
ignoring any force of tension from being tied to the tree, etc). Given these
properties, you can deduce that the force of gravity on the coat
is equal to the wind force.

The wind force is being applied across the entire 0.8 square meter cloak
with an air density mass of $1.229 kg / m^{3}$ and a speed
of 46.4922 meters per second (104 mph).

The gravitational force on the cloak is affected by
gravity that accelerates by 9.8 meters per second every second.

\begin{itemize}
\item $F_{wind} = ma$ on 0.8 square meters**
\item $F_{gravity\ on\ cloak} = mg$
\item $F_{wind} = F_{gravity\ on\ cloak}$***
\item $a_{wind} = \delta velocity / \delta time = m/s^{2} = v^{2}$****
\end{itemize}

\noindent What is the weight of the cloak?\\

\noindent \scriptsize \textbf{*} \textbf{``block the wind''} is not referring
to a fabric's ability to prevent air from moving
through the threads of fabric; just assume that the fabric is fully windproof
in this regard because of its tight threading.
What \textbf{``block the wind''} means here
is that the cloak is heavy enough that the wind won't move/lift/tilt the cloak
and the wind will
not be able to pass through any where that the cloak was previously hanging.

\noindent \scriptsize \textbf{**} F=ma (force equals mass times acceleration)
for wind assumes a default factor of
1 square meter area of impact: F = 1 * m * a. The cloak is not 1 square meter;
substitute in the area into the corrected formula version:\\ \indent
F = sq\_mtr\_area * m * a

\noindent \scriptsize \textbf{***} F=mg is another way to write F=ma when
dealing with gravity since g is the gravity acceleration constant

\noindent \scriptsize \textbf{****} m/s = v; meters per seconds is equal to velocity. Substitute v in place of m/s and acceleration becomes equal to v^{2}

\subsection*{EOTW 1}
\textit{ Set in The Eye of the World $>$ An Empty Road }  \pagebreak

\section*{What If There Were 2 More Months of Winter?}

Rand received a thick silver coin from Moraine,
with enough silver to buy a horse!

Rand and Tam's mare, Bela, was already able to get them safely
to Edmond's Field in time for Bel Tine, but let's roll back the months
and pretend to be in the past,
except Rand gets to keep this coin. He now has two months of winter left
before he will travel to Bel Tine with just enough money to buy a horse.

Bela's living configuration consists of an unshared stall enclosure
with a fence
that is not secured. A month back there were 1,000 horses total (including Bela) in the Two Rivers.
However the last winter month was brutal as can be shown in the ledger below,
and it is expected to continue that way for the 2 remaining winter months.

Rand has a few options. A safe option might be to keep the coin and just buy
another horse if Bela doesn't make it the 2 months, however, if enough horses
die then the price for the horses will go up which would prevent him from
being able to buy a horse. There will be a raising in price
if the population of horses gets below 700 (assume the ledger is a complete
listing of deaths and assume there are no new horse births). This is still
an option if the total loss rates from the ledger
are found to be favorable enough (assume the rate percentages will be exactly
as shown on the ledger for both upcoming months).

Another option is that Rand can buy a horse now, but since he won't have
any extra he will need Bela to share the enclosure and won't have enough
to secure it.

The last option is that Rand can buy tools to secure Bela's fence and
accept that he won't have enough to later buy another horse.

\vspace{14pt}
\indent \textbf{Last (Winter) Month Equine Head Count Ledger - Two Rivers}
\VerbatimInput{eotw2.tbl}

Which option gives Rand the most favorable odds
to have a horse available that can carry his father's (Tam) barrels
of ale for the Bel Tine celebration 2 months from now?
\begin{itemize}
\item[(1)] Keep the coin to possibly have money to buy a horse
if needed in 2 months ($U+0$ config)**
\item[(2)] Buy a stallmate for Bela right now ($U+1$ config)
  \item[(3)] Secure Bela's fence right now ($S+0$ config)
\end{itemize}

%1,000
% .06 = 43/723
% .11 = 79/723
% .02 = /277

\noindent \scriptsize \textbf{*} The S+1 configuration in the ledger is not an
option for Rand since he does not have enough to buy Bela a stallmate and
buy tools to secure Bela's enclosure. He can only do 1 or the other.

\noindent \scriptsize \textbf{**} Keeping the coin gives the worst odds
for Bela's enclosure configuration ($U+0$), so it will only beat the other
configurations
if it can be expected that after 2 months
the Two Rivers' horse population is $>= 700$ horses
(this is true because without price fluctuation Rand will get a guaranteed
``to-be-alive'' horse for his Bel Tine travels)

\subsection*{EOTW 2}
\textit{ Set in The Eye of the World $>$ Strangers }  \pagebreak

\section*{Attempted Solutions}

\subsection*{SLN EOTW -1}
\VerbatimInput{eotw-1.py}
\VerbatimInput{eotw-1.sln} \pagebreak

\subsection*{SLN EOTW 0}
\VerbatimInput{eotw0.py}
\VerbatimInput{eotw0.sln} \pagebreak

\subsection*{SLN EOTW 1}
\VerbatimInput{eotw1.py}
\VerbatimInput{eotw1.sln} \pagebreak

\subsection*{SLN EOTW 2}
\VerbatimInput{eotw2.py}
\VerbatimInput{eotw2.sln}


\end{document}
